\chapter{Safety Requirements}
\label{chap:safety-requirements}

The following relevant hazards were identified through the safety assessment process:

\begin{itemize}
\item H1:
      Prolonged exposure of Infant to unsafe heat or cold
      Classification: catastrophic
      Probability: $<10^{-9}$ per hour of operation
\end{itemize}

To ensure that probability of hazard H1 is $10^{-9}$ per hour of operation, the following derived
safety requirements are levied on the Isolette Thermostat:

\begin{itemize}
\item SR-1: The Isolette shall include an independent regulator function that maintains the
      Current Temperature inside the Isolette within the Desired Temperature Range.

      Rationale: The Desired Temperature Range will be set by the Nurse to the ideal range
      based on the Infant’s weight and health. The regulator should maintain the Current
      Temperature within this range under normal operation.

      Allowed probability of failure: $<10^{-5}$ per hour
\item SR-2: The Isolette shall include an independent monitor function that activates an Alarm
      within a maximum of 5 seconds whenever
  \begin{itemize}
  \item the Current Temperature falls below or rises above the Alarm Temperature Range.
  \item the Current Temperature or the Alarm Temperature Range is flagged as invalid.
  \item an internal failure has been detected in the monitor function.
  \end{itemize}
  Rationale: The Alarm Temperature Range will be set by the Nurse based on the Infant’s
  weight and health. The Infant should be removed from the Isolette within 15 seconds
  after the Current Temperature falls below or rises above this range. With the normal
  monitoring provided by the Nurse, this can be accomplished within 10 seconds, leaving 5
  seconds for the system to activate the Alarm. Activating the Alarm in less time is
  desirable.

  If the Current Temperature or the Alarm Temperature Range provided to the monitor
  function are flagged as invalid or if an internal failure is detected in the monitor function,
  the monitor function should not be trusted to perform correctly.

  Allowed probability of failure: $<10^{-5}$ per hour.
\end{itemize}